The Calculus of Linear Constructions

### 2021-10-12 writing/draft1.tex
draft

  We prove the following lemma to commute erasure and substitution when needed.
  \begin{lemma} Erasure commutes with substitution. \\ 
    For any CLC terms $m$, $n$, and some variable $x$, $\erase{m[n/x]} = \erase{m}[\erase{n}/x]$. 
  \end{lemma}

  For the following theorem, we refer to the reductions of CLC as $\pstep_{\scriptscriptstyle \text{CLC}}$, and the reductions of CC$\omega$ as $\pstep_{\scriptscriptstyle \text{CC$\omega$}}$.
  \begin{theorem} \label{preserve} Erasure preserves reduction. \\
    For any CLC terms $m$, and $n$, if there is $m \pstep_{\scriptscriptstyle \text{CLC}} n$, then there is $\erase{m} \pstep_{\scriptscriptstyle \text{CC$\omega$}} \erase{n}$.
  \end{theorem}

@@

  \section{Future Work}
  All of the theorems we have developed so far are purely syntactic in nature. But the natural correspondence between linear types and call-by-value semantics seem to hint at a deeper connection. Indeed, past works\cite{cbvsemantics} have provided insight for the simply typed case. We would like to extend these results our dependent linear type theory. 
  \section{Conclusion}

>>>>

  With slight overloading of notation, we define erasure for CLC contexts recursively.

  \begin{definition}
    \begin{align*}
      \erase{\epsilon} &= \epsilon \\
      \erase{\Gamma, x \stype{s} A} &= \erase{\Gamma}, x : \erase{A}
    \end{align*}
  \end{definition}

  We prove the following lemma to commute erasure and substitution whenever needed.
  \begin{lemma} Erasure commutes with substitution. \\ 
    For any CLC terms $m$, $n$, and some variable $x$, $\erase{m[n/x]} = \erase{m}[\erase{n}/x]$. 
  \end{lemma}

  For the following theorem, we refer to the reductions in CLC as $\pstep_{\scriptscriptstyle \text{CLC}}$, and the reductions in CC$\omega$ as $\pstep_{\scriptscriptstyle \text{CC$\omega$}}$.
  \begin{theorem} \label{preserve} Erasure preserves reduction. \\
    For any CLC terms $m$, and $n$, if there is $m \pstep_{\scriptscriptstyle \text{CLC}} n$, then there is $\erase{m} \pstep_{\scriptscriptstyle \text{CC$\omega$}} \erase{n}$.
  \end{theorem}

@@

  \section{Future Work}
  \section{Conclusion}
